Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-11-08 tex/MISDP-Presolving/MISDPpresolving.tex
typo
add more potenitallly usefull inequalities

@@

We apply the Perron-Frobenius theorem. To this end, we define a matrix $A$ to
be reducible if there exists a permutation matrix $P$ such that
\[
  P\T A P = \begin{pmatrix} B & C \\ 0 & D \end{pmatrix}.
\]
Otherwise it is \emph{irreducble}. We have the following:

@@

\paragraph{Two Valid SOCP Constraint}

>>>>

\paragraph{Bounds for Rank 1 Motivated Structures}

If the constraints contain
\[
  \begin{pmatrix}
    1 & x\T \\
    x & X
  \end{pmatrix}
  \succeq 0,
  \quad
  \ell \leq x \leq u,
\]
then Nohra et al.~\cite{NohRS20} propose the following inequalities for all
$i \in [n]$:
\begin{align*}
  X_{ii} & \geq 2\, \ell_i x_i - \ell_i^2,\\ 
  X_{ii} & \geq 2\, u_i x_i - u_i^2.
\end{align*}
For example, the validity of the first type can be seen as follows:
\[
  (x_i - \ell_i)^2 \geq 0 \quad\Leftrightarrow\quad x_i^2 \geq 2\,
  \ell_i x_i - \ell_i^2.
\]
Combining with the $2 \times 2$-minor inequality $X_{ii} - x_i^2 \geq 0$
yields the inequality. The inequality $X_{ii} \geq 2\, u_i x_i - u_i^2$
arises similarly.

The given inequalities are not yet implemented, but the results
in~\cite{NohRS20} suggest that they might be usefull if the LP-relaxation
is solved.

The above structure arises from relaxing quadratic problems. In this case,
additionally $X = x x\T$ and the rank of $X$ has to be 1. Then additional
inequalities have to hold, for example McCormick inequalities.

@@

We apply the Perron-Frobenius theorem. To this end, we define a matrix $A$ to
be \emph{reducible} if there exists a permutation matrix $P$ such that
\[
  P\T A P = \begin{pmatrix} B & C \\ 0 & D \end{pmatrix}.
\]
Otherwise it is \emph{irreducible}. We have the following:

@@

\paragraph{Two Valid SOCP Constraints}
